GPU Efficient Texture Based Bezier Curve Evaluation

### 2015-06-24 Paper/paper.tex
mathematical basis WIP

\documentclass{jcgt}
\usepackage{tikz}
\definecolor{darkgreen}{RGB}{0,192,0}

@@

TODO: this section.
TODO: show linear, bilinear, trilinear interpolation to be equivelant!  How to prove for N dimensions?

>>>>

\documentclass{jcgt}
\usepackage{tikz}
\usepackage{amsmath}
\definecolor{darkgreen}{RGB}{0,192,0}

@@

The De Casteljeau algorithm is equivelant to the Bernstein form of Bezier curves (\autoref{eqn:bernsteinform}) which means that the Bernstein form must be able to be eqvaluated by linear, bilinear, trilinear, and N-Linear interpolation.

\begin{equation}
\bf{P} = \sum\limits_{i=0}^n\binom {n} {i}s^{n-i}t^i\text{\bf{P}}_i
\label{eqn:bernsteinform}
\end{equation}

When n is 1, to make a linear Bezier curve, the equation we get out is in fact just linear interpolation (\autoref{eqn:bernsteinformn1}).  Note that in the Berntstein form, s is equivelant to 1-t.

\begin{equation}
\bf{P} = s*P_0 + t*P_1
\label{eqn:bernsteinformn1}
\end{equation}

When n is 2, to make a quadratic Bezier curve, things are not quite as obvious:

TODO: finish this section.
TODO: show linear, bilinear, trilinear interpolation to be equivelant!
TODO: How to prove for N dimensions?

\subsection{Accuracy}
